Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-20 automatica/paper.tex
section 8

%The \textit{acrobot}plant corresponds to the model of a two-link 
%underactuated robot manipulator, 
%named acrobot, 
%linearized by partial feedback linearization~\cite{acrobot}.
The \textit{antenna} benchmark (\#2) 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
%The \textit{ballmaglev}  plant corresponds to the model of a simple 
%eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
The \textit{bioreactor} benchmark  is a linear model 
%identified by least squares 
of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.

The \textit{Chen\_ex1} and \textit{Chen\_ex3}
benchmarks correspond to high-order control system 
%discrete 
models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}. 
The benchmarks \textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} deal with 
automotive cruise control models, where control is used to keep 
constant the speed of an automobile, tracking a desired speed reference, and compensating disturbances and uncertainties. % related to relief and terrain.

%There are two continuous stirred tank reactor models named 
\textit{cstr}  and \textit{cstrtmp}  describe the PH dynamics of a reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a reaction~\cite{astrom2006advanced} in a 
%continuous flow stirred-
tank reactor. The \textit{DC motor} plant  describes the velocity 
dynamics of a 
%basic brushed 
direct-current electrical machine.

%The \textit{Flexbeam} benchmark  is 
%a plant 
%employed in vibration studies and models  
%the physical system consists of 
%a flexible metallic structure with sensors and actuators. 
The \textit{guidance chen} benchmark ( is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
model-order reduction techniques; it models a guidance control system, 
which is used to determine the path of an autonomous vehicle. 
The \textit{helicopter} benchmark plant  describes the transitional and rotational dynamics 
%of transitional motion with respect to a longitudinal plane and the rotational motion around the longitudinal axis for 
of a coaxial helicopter.

%\textit{Invpendulum\_cartpos}  and 
The \textit{Invpendulum\_pendang}  
describes a model for the cart position and the angle of an inverted pendulum placed on the cart,  
%plant composed by a point mass, which must be equilibrated above the pivot point and is mounted on an one degree of freedom cart that 
which moves over a track through a DC motor.

The \textit{magpointer}  describes a magnetic pointer, 
% plant composed by a pointer employed in analogue gauges and indicators, 
whose angular position dynamics is controlled by a magnetic field. 
The \textit{magsuspension} describes  the dynamic of a magnetic car suspension system. 
The \textit{pendulum}  plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.

The \textit{Regulator} consists of a linear model of a synchronous electrical machine% connected to an infinite bus
~\cite{KOKOTOVIC198023}. 
The \textit{springer-mass damper system} plant is a standard model for the dynamics of several mechanical systems. 
%This benchmark describes a mass, which is fixed to a node by means of a springer and moves under the action of an input force, damping, and elastic force.
The \textit{steam drum} benchmark describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}.

The \textit{suspension} models a single-wheel suspension system of a car, 
namely the relative motion dynamics of a mass springer damp model, which connects the car to one of its wheels.  
The \textit{tapedriver} benchmark  models a computer tape driver, 
that is a computer storage device used to read and write data on magnetic tapes.

@@

\begin{table*}
\centering
\begin{tabular}{| l | c | c | r | c | r |}
%
\hline
% \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Run-time} \\
 Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time \\\hline
%1  & Acrobot     & 4 & 16,8 & 61529.8\,s &  & ~\xmark \\
 Antenna     & 6 &  & ~\xmark & 16,10 & 817.4\,s \\
%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
 Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &23.6\,s \\
 Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 12.7\,s \\
%4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
 Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 59.1\,s \\
%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
 Cruise      & 1 & 16,8 & 9.7\,s & 16,10 & 10.3\,s \\
 CruiseHSCC & 1 & 16,8 & 9.7\,s & 16,10 & 10.3\,s  \\
 Cstr & 3 & & ~\xmark & 16,10 & 21.4\,s \\
 Cstrtmp  & 3 & 16,8 & 12.5\,s &16,10 & 15.4\,s \\
 DCmotor   & 2 & 16,8  & 10.0\,s & 16,10 & 11.4\,s  \\
%11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
 Helicopter   & 3 &  & ~\xmark & 16,10 & 32.0\,s \\
%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
 Invpendulum\_pendang & 2 & 16,8  & 10.7 & 16,10 & 14.8\,s\\
 Magpointer   & 2 &  & ~\xmark & 16,10 & 86.0\,s \\
 Magsuspension  & 2 & 12,12  & 39.0\,s  & 16,10 & 43.2\,s \\
 Pendulum   & 2 & 16,8 & 13.2\,s & 16,10 & 16.6\,s\\
 Regulator   & 5 & 16,8 & 1532.7\,s & 16,10 & 999.6\,s\\
 Springmassdamper & 2 & & ~\xmark &16,10 & 24.2s \\
 Steamdrum   & 3 & 16,8  & 700.9s & 16,10 & 24.4\,s \\
 Suspension  & 4 & 16,8  & 11.4\,s & 16,10 &15.4\,s \\
 Tapedriver   & 3 & 16,8  & 11.4\,s &16,10 & 13.3\,s \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}

>>>>

%The \textit{acrobot}plant corresponds to the model of a two-link 
%underactuated robot manipulator, 
%named acrobot, 
%linearized by partial feedback linearization~\cite{acrobot}.
The \textit{antenna} benchmark (\#2) 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. \\
%The \textit{ballmaglev}  plant corresponds to the model of a simple 
%eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
The \textit{bioreactor} benchmark is a linear model 
%identified by least squares 
of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.\\ 
The \textit{Chen\_ex1} and \textit{Chen\_ex3}
benchmarks correspond to higher-order control system 
%discrete 
models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}.  \\
The benchmarks \textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} deal with automotive cruise control models, 
where the control is used to maintain the speed of an automobile constant, 
tracking a desired speed reference, and compensating disturbances and uncertainties. \\ % related to relief and terrain. 
%There are two continuous stirred tank reactor models named 
\textit{cstr}  and \textit{cstrtmp}  describe the pH dynamics of a reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a reaction~\cite{astrom2006advanced} in a 
%continuous flow stirred-
tank reactor. \\ 
The \textit{DC motor} plant  describes the velocity 
dynamics of a 
%basic brushed 
direct-current electrical machine. \\ 
%The \textit{Flexbeam} benchmark  is 
%a plant 
%employed in vibration studies and models  
%the physical system consists of 
%a flexible metallic structure with sensors and actuators. 
The \textit{guidance chen} benchmark ( is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
model-order reduction techniques; it models a guidance control system, 
which is used to determine the path of an autonomous vehicle \note{This is similar to the two benchmarks above?}. \\ 
The \textit{helicopter} benchmark plant  describes the transitional and rotational dynamics 
%of transitional motion with respect to a longitudinal plane and the rotational motion around the longitudinal axis for 
of a coaxial helicopter. \\ 
%\textit{Invpendulum\_cartpos}  and 
The \textit{Invpendulum\_pendang}  
describes a model for the cart position and the angle of an inverted pendulum placed on the cart,  
%plant composed by a point mass, which must be equilibrated above the pivot point and is mounted on an one degree of freedom cart that 
which moves over a track through a DC motor. \\ 
The \textit{magpointer}  describes a magnetic pointer, 
% plant composed by a pointer employed in analogue gauges and indicators, 
whose angular position dynamics is controlled by a magnetic field. \\ 
The \textit{magsuspension} describes  the dynamic of a magnetic car suspension system. \\
The \textit{pendulum}  plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.  \\ 
The \textit{Regulator} consists of a linear model of a synchronous electrical machine% connected to an infinite bus
~\cite{KOKOTOVIC198023}. \\
The \textit{springer-mass damper system} plant is a standard model for the dynamics of several mechanical systems. \\ 
%This benchmark describes a mass, which is fixed to a node by means of a springer and moves under the action of an input force, damping, and elastic force.
The \textit{steam drum} benchmark describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}. \\ 
The \textit{suspension} models the single-wheel suspension system of a car, 
namely the relative motion dynamics of a mass-spring-damper model, which connects the car to one of its wheels.  \\
The \textit{tapedriver} benchmark models a computer tape driver, 
that is a computer storage device used to read and write data on magnetic tapes.

@@

\begin{table*}
\centering
\begin{tabular}{| l | c | c | r | c | r |}
%
\hline
% \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Run-time} \\
 Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time \\\hline
%1  & Acrobot     & 4 & 16,8 & 61529.8\,s &  & ~\xmark \\
 Antenna     & 6 &  & ~\xmark & 16,10 & 817.4\,s \\
%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
 Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &23.6\,s \\
 Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 12.7\,s \\
%4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
 Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 59.1\,s \\
%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
 Cruise      & 1 & 16,8 & 9.7\,s & 16,10 & 10.3\,s \\
 CruiseHSCC & 1 & 16,8 & 9.7\,s & 16,10 & 10.3\,s  \\
 Cstr & 3 & & ~\xmark & 16,10 & 21.4\,s \\
 Cstrtmp  & 3 & 16,8 & 12.5\,s &16,10 & 15.4\,s \\
 DCmotor   & 2 & 16,8  & 10.0\,s & 16,10 & 11.4\,s  \\
%11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
 Helicopter   & 3 &  & ~\xmark & 16,10 & 32.0\,s \\
%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
 Invpendulum\_pendang & 2 & 16,8  & 10.7 & 16,10 & 14.8\,s\\
 Magpointer   & 2 &  & ~\xmark & 16,10 & 86.0\,s \\
 Magsuspension  & 2 & 12,12  & 39.0\,s  & 16,10 & 43.2\,s \\
 Pendulum   & 2 & 16,8 & 13.2\,s & 16,10 & 16.6\,s\\
 Regulator   & 5 & 16,8 & 1532.7\,s & 16,10 & 999.6\,s\\
 Springmassdamper & 2 & & ~\xmark &16,10 & 24.2s \\
 Steamdrum   & 3 & 16,8  & 700.9s & 16,10 & 24.4\,s \\
 Suspension  & 4 & 16,8  & 11.4\,s & 16,10 &15.4\,s \\
 Tapedriver   & 3 & 16,8  & 11.4\,s &16,10 & 13.3\,s \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results \note{expand description (short, crisp)}\label{tab:results}}
\end{table*}
